Exploiting First-Class Arrays in Fortran for Accelerator Programming

### 2010-12-15 opencl/papers/source-to-source.tex
more verbatim

Array syntax transforms nearly directly to OpenCL code.  For example, interior
variables are particularly straightforward as they as scalar quantities in
OpenCL,
\begin{verbatim}
   iH = iH + (dt/dx) * ( region(Ux, face_lt) - region(Ux, face_rt) )
           + (dt/dy) * ( region(Vy, face_dn) - region(Vy, face_up) );
\end{verbatim}

Region variables are more complicated because they are arrays.
\begin{verbatim}
   Hx[l] = 0.5 * ( region(H_local, face_lt) + ... );
\end{verbatim}
where {\tt l = LX + LY*(NLX+halo(0)+halo(1)))} is a local index variable, {\tt
  LX = get\_local\_id(0)} is the local thread id in the $x$ dimension, {\tt LY =
  get\_local\_id(1)} is the local thread id in the $y$ dimension, {\tt NLX =
  get\_local\_size(0)} is the size of the thread group in the $x$ dimension, and
the {\tt get\_local\_id} and {\tt get\_local\_size} functions are defined by the
OpenCL compiler.

>>>>

Array syntax transforms nearly directly to OpenCL code.  For example, interior
variables are particularly straightforward as they as scalar quantities in
OpenCL,

{\small
\begin{verbatim}
iH = iH + (dt/dx) * (region(Ux, face_lt) - 
                     region(Ux, face_rt) )
        + (dt/dy) * (region(Vy, face_dn) - 
                     region(Vy, face_up) );
\end{verbatim}
}

Region variables are more complicated because they are arrays.

{\small
\begin{verbatim}
Hx[l] = 0.5 * (region(H_local, face_lt)+ ...);
\end{verbatim}
}

where {\tt l = LX + LY*(NLX+halo(0)+halo(1)))} is a local index variable, {\tt
  LX = get\_local\_id(0)} is the local thread id in the $x$ dimension, {\tt LY =
  get\_local\_id(1)} is the local thread id in the $y$ dimension, {\tt NLX =
  get\_local\_size(0)} is the size of the thread group in the $x$ dimension, and
the {\tt get\_local\_id} and {\tt get\_local\_size} functions are defined by the
OpenCL compiler.
